A systematic search for transiting planets using \KT

### 2015-02-06 ms.tex
adding tables and a few words about injections

\usepackage{color,hyperref}
\definecolor{linkcolor}{rgb}{0,0,0.5}
\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
            filecolor=linkcolor,urlcolor=linkcolor}
\usepackage{url}
\usepackage{amssymb,amsmath}
\usepackage{subfigure}

@@

@@

@@

>>>>

\usepackage{color,hyperref}
\definecolor{linkcolor}{rgb}{0,0,0.5}
\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
            filecolor=linkcolor,urlcolor=linkcolor}
\usepackage{url}
\usepackage{amssymb,amsmath}
\usepackage{subfigure}
\usepackage{booktabs}

@@

\section{Performance}

To test the performance of our method, we conducted a suite of XXXX injection
and recovery tests.
For each test, we inject the signal from a realistic planetary system into the
raw aperture photometry and passed it through the full pipeline.
These synthetic systems have periods and radius ratios drawn uniformly in
\dfmtodo{some range} and uniformly distributed impact parameters and phases.
The eccentricities are drawn from a beta distribution with \dfmtodo{some
parameters; cite Kipping} and the multiplicity is set to match the observed
multiplicity distribution in the KOI catalog \dfmtodo{cite}.
MA limb darkening, exposure time integration, etc.

After running these light curves with injections through the full pipeline, if
the resulting period and phase of the recovered signal were within YYYY of the
true injected values, we deemed the injection a success.
Figure ZZZZ shows the fraction of recovered signals as a function of the
physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.

@@

\subsection{Planet candidates}

\subsection{Probable binaries}

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/completeness.pdf}
\end{center}
\caption{%
\figlabel{completeness}}
\end{figure}

\begin{table}[p]
\begin{center}
\small
\include{tab-cand}
\end{center}
\caption{%
Candidates
\tablabel{cand}}
\end{table}

\begin{table}[p]
\begin{center}
\include{tab-eb}
\end{center}
\caption{%
Probable binaries.
\tablabel{eb}}
\end{table}
